Predicting Audio Features with Last.fm Tags

### 2023-04-06 paper/main.tex
analyzing results for paper
writing

@@

>>>>

The mean and standard deviation for each variable are as follows:

\begin{table}[h]
      \begin{center}
      \begin{minipage}{\textwidth}
      \caption{Audio features description}\label{audio_features_stats}%
      \begin{tabular}{@{}lll@{}}
      \toprule
      Feature           & $\mu$ & $\sigma$ \\
      \midrule
      Danceability      & 0.599  & 0.193  \\
      Energy            & 0.631  & 0.233  \\
      Acousticness      & 0.221  & 0.302  \\
      Instrumentalness  & 0.514  & 0.382  \\
      Valence           & 0.435  & 0.279  \\
      \botrule
      \end{tabular}
      \end{minipage}
      \end{center}
\end{table}

Figure \ref{fig:audio_features_distribution} represents the density function of each variable.

\begin{figure}[h!]
      \centering
      \includegraphics[width=\textwidth]{images/features-distribution.png}
      \caption{Distribution of audio features}
      \label{fig:audio_features_distribution}
\end{figure}

We can compare our single-user data with a bigger audio features dataset https://www.kaggle.com/datasets/tomigelo/spotify-audio-features.
This dataset shows similar data distributions.

I have posted a question on the Spotify Developer forum, relative to the release of a dataset 
https://community.spotify.com/t5/Spotify-for-Developers/May-I-publish-an-open-source-dataset-that-contains-Spotify-Audio/td-p/5529259

@@

\subsection{Experiments Execution and Results}

The experiments:

\begin{table}[h]
      \begin{center}
      \begin{minipage}{\textwidth}
      \caption{Experiment results. Cells values correspond to the RMSE value.}\label{experiment_results}%
      \begin{tabular}{@{}llllll@{}}
      \toprule
      Experiment                           & Danceability    & Acousticness    & Energy    & Valence    & Instrumentalness \\
      \midrule
      $Base_token_{weight}$
      $XGBoost_Tags_{energy}$                        & 300   \\
      XGBoost - $y_{energy}$           & 300   \\
      XGBoost - Tokens - Weight Repeat     & 300   \\
      \botrule
      \end{tabular}
      \footnotetext[1]{Tolerance for the stopping criteria.}
      \end{minipage}
      \end{center}
\end{table}

\subsubsection{Results for Tabular Data Models}

\begin{figure}[h!]
      \centering
      \includegraphics[width=0.5\textwidth]{images/rmse_by_model_and_limit.png}
      \caption{RMSE mean and standard deviation by model and tags/tokens limit.}
      \label{fig:rmse_by_model_and_limit}
\end{figure}

\begin{figure}[h!]
      \centering
      \includegraphics[width=0.7\textwidth]{images/rmse_by_model_and_feature.png}
      \caption{RMSE mean and standard deviation by model and audio feature.}
      \label{fig:rmse_by_model_and_feature}
\end{figure}

\begin{figure}[h!]
      \centering
      \includegraphics[width=0.7\textwidth]{images/rmse_by_model_and_input.png}
      \caption{RMSE mean and standard deviation by model and input type (tag probablities or tokens).}
      \label{fig:rmse_by_model_and_input}
\end{figure}

\begin{figure}[h!]
      \centering
      \includegraphics[width=0.7\textwidth]{images/rmse_by_feature_and_input.png}
      \caption{RMSE mean and standard deviation by audio feature and input type (tag probablities or tokens).}
      \label{fig:rmse_by_feature_and_input}
\end{figure}
